A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-16 paper.tex
Tweak wording

\subsection{Unsubscribe to Data Products}
When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}. $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription. In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage. However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied. Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data. The new key should be updated for the remaining subscribers.
\begin{align}
    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
\end{align}
\subsection{Refund}
\label{section:refund}
The refund topics is complicated in a subscription services, therefore, we illustrated the challenges in this section. As the subscription-based services in real world, participants can launch a refund in following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee. However, issues such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully. Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers. If they can't reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product. Third, the refund could launch by providers when they can't maintain products as committed.

\section{Evaluations}
\label{section:evaluation}
We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract. 2) Evaluate the cost of adopting MAM on devices, since it is the most commonly used component to data provider.

@@

Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform. The time of RPi distributed widely, from 5 secs to over 2500 secs, since the randomness of PoW has huge impact. The simulation results indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios. Therefore, the low-level devices can delegate MAM operations to Accels while ensuring the profit and privacy of providers through E2EE can effectively solve performance problems and lower the threshold to participate in such framework. Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi. However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.

@@

However, this work has a main focus on the subscription-based model and relative experiments. Consequently, the next step is extending the work to:
\begin{enumerate}
	\item reduce the use of Gas in key exchange process and consider the possibility of the zero-knowledge protocol to lower transaction costs
	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism
	\item develop a searching engine for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
\end{enumerate}

>>>>

\subsection{Unsubscribe to Data Products}
When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}. $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription. In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage. However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied. Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data. The new key should be updated for the remaining subscribers.
\begin{align}
    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
\end{align}
\subsection{Refund}
\label{section:refund}
The refund topics is complicated in a subscription services, therefore, we illustrated the challenges in this section. As the subscription-based services in real world, participants can launch a refund in following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee. However, issues such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully. Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers. If they can not reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product. Third, the refund could launch by providers when they fail to maintain products as committed.

\section{Evaluations}
\label{section:evaluation}
We evaluate the cost of operating the subscription-based data trading infrastructure in two aspects: 1) Evaluate the minimum cost for participants to sustain or subscribe to a data product via Product Contract. 2) Evaluate the cost of adopting MAM on arbitrary devices, since it is the most commonly used component to data provider.

@@

Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform. The time of RPi distributed widely, from 5 secs to over 2500 secs, since the randomness of PoW has huge impact. The simulation results indicate that MAM is difficult for low-level sensor devices to run, whereas these kind of devices are the majority hardware in the IoT scenarios. Therefore, the low-level devices can delegate MAM operations to Accels while ensuring the profit and privacy of providers through E2EE can effectively solve performance problems and lower the threshold to participate in such framework. Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi. However, MAM operations are fairly time-consuming, and improving the performance of MAM is an essential issue that needs to be done for the next step.

@@

Our work has a main focus on the subscription-based model and relative experiments. And the next step is extending it to:
\begin{enumerate}
	\item reduce the use of Gas in key-agreement protocol and consider the possibility of the zero-knowledge proof to lower transaction costs;
	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism;
	\item develop a product portal for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
\end{enumerate}
